

\documentclass{resume}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page

\usepackage[hidelinks]{hyperref}

\begin{document}

\name{GRAHAM BARADOY\\[12pt]}

\address{\href{http://grahambaradoy.com}{grahambaradoy.com} \\ \href{https://www.github.com/baradoy}{github.com/baradoy}}
\address{ \href{mailto:graham@baradoy.ca}{graham@baradoy.ca} \\ 250-216-7112 }

\begin{resume}

\section{}
    Writing software is a craft, I aim to be a master craftsman.
    My goal is to have the work I do have a positive influence on people's lives.
    I am a strategic thinker focused on balancing immediate objectives with the long term payoffs of building a quality product.

\section{EXPERIENCE}

    % Contracting %
     \vspace{+0.1in}
    \begin{tabular}[t]{@{}l}
        {\bf Senior Elixir Developer} Contractor
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        April 2019 -- Present
    \end{tabular}\\
    I look for contracts that have a positive impact on society.
    I supported multiple projects from early and mid stage to launch, including improving health care flows, social network platform for female entrepreneurs, and services for indigenous communities.
    \vspace{+0.05in}
    \begin{itemize} \itemsep -2pt
    \item Leading small teams building quality products, building the most important things and avoiding expensive distractions. Collaborating with stakeholders to bring products from inception to launch in a short time.
    \item Mentoring team members. Promoting positive team culture and advocating for process improvements, such as early collaboration and a focus on the end user experience.
    \item Principal contributor with Elixir, Phoenix, LiveView, Postgres, and GraphQL. Responsible for and contributing to key architecture and data structures decisions.
    \item Contributing to projects with Vue, Rails, React, AlpineJS, and Tailwind
    \end{itemize}


    % Covault %
    \vspace{+0.1in}
    \begin{tabular}[t]{@{}l}
        {\bf VP of Software Development} Covault Inc.
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        March 2018 -- March 2019
    \end{tabular}\\
    I took Covault's platform from a vision and an early prototype to a well executed product. I worked with Covault leadership to define product direction and roadmap.
    \vspace{+0.05in}
    \begin{itemize} \itemsep -2pt
    \item Incorporating customer feedback, I focused the product direction in a way that increased the value of the product for all parties.
    \item Owned technical direction and strategy working to create Covault's product as a GraphQL, Elixir and React stack.
    \item Set clear goals and expectations for development for a small team. Promoted work life balance while ensuring rapid development of Covault's product and team satisfaction.
    \item Principal contributor, implemented and maintained critical components of the Elixir / GraphQL backend.
    \end{itemize}

    % Lightrail %
    \vspace{+0.1in}
    \begin{tabular}[t]{@{}l}
        {\bf Director of Development} Lightrail, Giftbit Inc.
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        August 2016 -- February 2018
    \end{tabular}\\
    As part of the Senior Management Team, I was involved in the planning and execution of our business strategy.
    I maintained an ongoing dialog with other senior leaders, giving them insight into Lightrail development, and other technology research findings.
    \vspace{+0.05in}
    \begin{itemize} \itemsep -2pt
    \item Lightrail product consists of several Grails services on AWS ECS, with AWS Lambda nano services consuming Kinesis Streams. Effective logging, alarming, monitoring and secure authorization and authentication exist across all parts of the system. A React/Redux app sits on top of the API powering the front end.
    \item Headed architecture and development for new product, lead dev teams in launching the product within a year. Negotiated technical cost to meet business needs.
    \item Principal contributor, implemented and maintained the core transaction functionality. Developed Lambda services including load testing and Kinesis stream event processing.
    \item Allocated time effectively for 6 direct reports, promoted work/life balance while ensuring business needs were met, including during overtime pushes.
    \end{itemize}

   \newpage

    % Rewards %
    \begin{tabular}[t]{@{}l}
        {\bf Engineering Team Lead} Rewards, Giftbit Inc.
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        October 2012 -- August 2016
    \end{tabular}
    \begin{itemize} \itemsep -2pt
    \item Built startup's first product as part of initial two developer team. Performed well under high pressure and tight deadlines.
    \item Developer across the full stack from front end to datastore. Stack included Coffeescript, Grails and MySql.
    \item Responsible for cloud based infrastructure and devops.
    \item Lead a fullstack team, up to 4 developers at a time. Hired, trained and mentored coops.
    \item Participated in TechStars startup program in Seattle 2015.
    \end{itemize}

    % Binary Rebellion %
    \begin{tabular}[t]{@{}l}
        {\bf Lead Designer, Developer} Binary Rebellion
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        September 2009 -- December 2012
    \end{tabular}
    \begin{itemize} \itemsep -2pt
    \item Worked with a small team to build a iOS game in the early days of iOS
    \item One of two principal contributors to the code base including developing the game engine in C for iOS
    \item Lead the design of game mechanics for Ninja Dino Showdown
    \end{itemize}

    % Science Alberta Foundation %
    \begin{tabular}[t]{@{}l}
        {\bf Project Coordinator} Science Alberta Foundation
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        October 2011 -- April 2012
    \end{tabular}
    \begin{itemize} \itemsep -2pt
    \item Managed several small educational digital projects
    \item Led user acceptance testing in participating schools
    \item Organized and maintained SAF’s digital assets catalog
    \item Assisted in maintenance and deployments of physical kiosks
    \end{itemize}

    % IBM %
    \begin{tabular}[t]{@{}l}
        {\bf DB2 Performance Benchmarking, Co-op Student} IBM Canada
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        May 2008 -- August 2009
    \end{tabular}
	\begin{itemize} \itemsep -2pt
    \item DB2 Performance Benchmarking, Co-op Student
    \item Developed and supported performance benchmark kit for DB2
    \item Performance and design validation on IBM’s Balanced Warehouse
    \item Diagnosed performance issues on Linux and AIX systems
    \end{itemize}

\section{EDUCATION}
    % Masters %
    \vspace{+0.1in}
    \begin{tabular}[t]{@{}l}
        {\bf Master of Science} University of Calgary
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        July 2010 - April 2012
    \end{tabular}
    \begin{itemize} \itemsep -2pt
    \item Thesis: A Physiological Feedback Controlled Exercise Video Game
    \end{itemize}

    % Beachelors %
    \begin{tabular}[t]{@{}l}
        {\bf Bachelor of Science with Honours in Computer Science}
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        September 2004 - April 2010
    \end{tabular}
    \begin{itemize} \itemsep -2pt
    \item Graduated with First Class Honours
    \item 16 month internship at IBM
    \end{itemize}

    \begin{tabular}[t]{@{}l}
       {\bf Awards  }
    \end{tabular}\vspace{+0.05in}
    \begin{itemize} \itemsep -2pt
    \item Queen Elizabeth II Graduate Scholarship  	2010, 2011
    \item NSERC Undergraduate Student Research Award	2006, 2007, 2008
    \end{itemize}

    \begin{tabular}[t]{@{}l}
        {\bf Research Assistant Experience  }
    \end{tabular}\vspace{+0.05in}
    \begin{itemize} \itemsep -2pt
    \item Virtual Reality Research Lab, University of Calgary	February 2010 – December 2012
    \item Web Data Management Lab, University of Calgary	February 2007 - May 2008
    \item Virtual Reality Research Lab, University of Calgary	 May 2006 - September 2006
    \end{itemize}



\section{OTHER EXPERIENCE}
    \vspace{+0.1in}
    \begin{tabular}[t]{@{}l}
        {\bf Founder, Organizer   } Whisky Oriented Development
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        January 2014 - Current
    \end{tabular}
    \begin{itemize} \itemsep -2pt
    \item Organize networking events for developers in the form of whisky tastings
    \end{itemize}

    \begin{tabular}[t]{@{}l}
        {\bf Bounty Snake Contributor   } Battle Snake
    \end{tabular}\vspace{+0.05in}
    \hfill
    \begin{tabular}[t]{l@{}}
        2016, 2017
    \end{tabular}
    \begin{itemize} \itemsep -2pt
    \item Contributed to the community event BattleSnake. Developed a “Bounty Snake” for contestants to compete against
    \end{itemize}

\end{resume}
\end{document}
